
\documentclass[11pt,a4paper,sans]{moderncv} 

\moderncvstyle{classic}
\moderncvcolor{burgundy} 
\usepackage{lipsum} 
\usepackage{amsmath}
\usepackage[scale=0.75]{geometry}

\firstname{Jaismin}
\familyname{Kaur}

\title{Sophomore, CSE  IIT Kanpur}
\email{jaismin@iitk.ac.in}
\mobile{+91 7027222722}
\homepage{staff.org.edu/~jsmith}{home.iitk.ac.in/$\sim$jaismin}
\extrainfo{\emailsymbol\emaillink{jaismin07@gmail.com}}


\begin{document}

\makecvtitle 


\section{Education}

\cventry{2015--2019(expected)}{Bachelor of Technology, Computer Science and Engineering}{Indian Institute of Technology, Kanpur}{}{\textit{CPI -- 9.5/10.0}}{}
\cventry{2015}{Central Board of Secondary Eduction}{St. Theresa's Convent Sr. Sec. School}{Karnal}{\textit{Percentage -- 94.00\%{}}}{}{\textbf{}}
\cventry{2013}{Central Board of Secondary Eduction}{Central Board of Secondary Eduction}{KArnal}{\textit{CGPA -- 10.0/10.0}}{}


\section{Achievements}

\cvitem{IIT JEE 2015}{\textbf{All India Rank 717} in JEE ADVANCED 2015 out of 150,000 students.}

\cvitem{KVPY 2014--15}{\textbf{Kishore Vaigyanik Protsahan Yojana}. Selected for KVPY scholarship through an exam and interview.}

\cvitem{NTSE 2013--14}{\textbf{National Talent Search Examination} got selected for NTSE scholoship through a two level examination.}

\cvitem{NSEP 2014}{\textbf{National Standard Examination in Physics}. got selected in top 1 \%{}}
\cvitem{Galaxy 2016}{\textbf{Best Artist} award in cultural fest, Galaxy 2016 IIT Kanpur.
}


\section{Experience}

\cventry{May,2016--July,2016}{Archetypal Analysis}{did a reading assignment on datat clustering and archetypal analysis on machine learning and data mining}{}{}{}{}
\cventry{January,2016--April,2016}{Analysis and Experimenting Randomised Algorithms}{did a project to experiment and analyse randomised quick sort, skip list, ,random walk, randomly built binary search tree, miller rabin test and PIT}{}{}{}{}
\cventry{August,2016--November,2016}{Furnichair}{manufactured a prototype model of a bench tht could convert into a table, double seater, side table with chair, bed and a table in TA201 course}{}{}{}


\section{Technical skills}

\cvitem{Programming Languages}{GO, Python, Java, C, HTML/CSS, JavaScript}
\cvitem{Tools}{Git, Latex, Excel, Word}
\cvitem{IDEs}{NetBeans, AndroidStudio}


\section{Relevant Courses}

\cvitem{}{Introduction to Programming \hfill Real Analysis \newline
		Linear Algebra and ODE \hfill Discrete Mathematics \newline
        Logic in Computer Science \hfill Abstract Algebra \newline
        Introduction to Electronics \hfill Introduction to Electrical Engineering \newline
        Computer Organisation\textsuperscript{*} \hfill Data Structures and Algorithms\textsuperscript{*} \newline
        \textsuperscript{*}ongoing courses
        }


\section{Position of Responsibility}

\cvitem{2016--present}{\textbf{Student Guide} from July 2016 till present.}
\cvitem{2016--present}{\textbf{Academic Mentor} from July 2016 till present.}
\cvitem{2016--present}{\textbf{Secretary, Fine Arts Club} from July 2016 till present.}


\section{Interests}

\renewcommand{\listitemsymbol}{-~}
\cvlistitem{Algorithms and Data Structures}
\cvlistitem{Artificial Inteligence}
\cvlistitem{Machine Learning}
\cvlistitem{Fine Arts and being creative!}
\cvitem{interested in}{google cloud platform and app engine.}


\end{document}
